pipeComp - Supplementary Methods

### 2020-05-12 supplementary_figures/supp_framework/supp_framework_explanations.Rmd
fixed typo

`r Rpackage("pipeComp")` is _not_ a general pipeline/workflow framework like, for instance, `r CRANpkg("drake")`, which boasts an impressive array of features (object histories and dependencies, caching and recovery, etc.). Instead, `r Rpackage("pipeComp")` was specifically designed for benchmarking: it makes benchmarks easily deployable, modifiable and extendable by encapsulating together abstract pipeline structures and evaluation procedures, and facilitates running many combinations of step parameters through hierarchical branching.

>>>>

`r Rpackage("pipeComp")` is _not_ a general pipeline/workflow framework like, for instance, `r CRANpkg("drake")`, which boasts an impressive array of features (object histories and dependencies, caching and recovery, etc.). Instead, `r Rpackage("pipeComp")` was specifically designed for benchmarking: it makes benchmarks easily deployable, modifiable and extensible by encapsulating together abstract pipeline structures and evaluation procedures, and facilitates running many combinations of step parameters through hierarchical branching.
